$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-27 paper/e6ssm-tuning-paper.tex
Added comment explaining that derivatives come straight from EWSB conditions (rather than including trivial extra equations), changed newlines \ \ to \

below.\\ \\

@@

where $m_t^2=y_t^2v_2^2/2$ and $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$. By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\ \\

@@

Written in the form of Eq. (\ref{eq:E6MZequation}) we see the

@@

right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel

@@

can be made even clearer by writing Eq. (\ref{eq:E6MZequation}) in the

@@

%% \section{\label{sec:tuning}Fine Tuning}
% Introduce tuning measure - BG measure (maybe Peter will add in a justification
% here).
% Explain that we derived the master formula in the E6SSM as given in Maien's 
% paper, but including extra effects not in that formula. 
% Full result is given in appendix.
% Numerical technique for calculating 1-loop tunings and including RG effects
% Outline is given here, full equations for RGE effects etc. given in appendix.
% How we calculate the tuning using spectrum generator, for E6SSM uses
% FlexibleSUSY (cite FlexibleSUSY and SARAH).

@@

Eq. (\ref{eq:E6masterformula}).\\ \\ However, it is well known in the

@@

Eq. (\ref{eq:E6EWSBConditions}), rather than
Eq. (\ref{eq:E6MZequation}). The general procedure that we use is as follows

@@

with $M_h^2$, are easily calculated analytically. The remaining
derivatives $\partial q_k /\partial p$ must be determined using the

@@

v_i/\partial p$ and $\partial q_k/\partial p$. Radiative corrections
may be easily incorporated by including the Coleman-Weinberg potential
contributions in the EWSB conditions.\\ \\ Evaluating the derivatives

@@

As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm} the severity of the tunings varies quite
a bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These charges change the
value of the coefficient $d$ in Eq. (\ref{eq:originalE6MZequation}).
The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
is $\{-0.01, 0.40, 0.50, 0.81 \}$ for $\{U(1)_I, U(1)_N, U(1)_\psi,
U(1)_\eta \}$ and this determines which of the models are most tuned.

@@

with $f_1,f_2,f_3$ as given in Eq. (\ref{eq:E6EWSBConditions}). The relevant partial derivatives are

@@

It is straightforward to compute the appropriate derivatives directly from the EWSB conditions (\ref{eq:E6EWSBConditions}). Similarly, the quantity $C$ appearing in Eq. (\ref{eq:E6masterformula}) is given by

@@

approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}).  For a

@@

diagonal, and the gaugino masses are taken to be real.\\ \\ In the

>>>>

below.\\

@@

where $m_t^2=y_t^2v_2^2/2$ and $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$. By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\

@@

Written in the form of Eq.~(\ref{eq:E6MZequation}) we see the

@@

right-hand side of Eq.~(\ref{eq:E6MZequation}) must be tuned to cancel

@@

can be made even clearer by writing Eq.~(\ref{eq:E6MZequation}) in the

@@

@@

Eq.~(\ref{eq:E6masterformula}).\\
However, it is well known in the

@@

Eq.~(\ref{eq:E6EWSBConditions}), rather than
Eq.~(\ref{eq:E6MZequation}). The general procedure that we use is as follows

@@

with $M_h^2$, are easily calculated by differentiating the conditions in Eq.~(\ref{eq:E6EWSBConditions})
with respect to the VEVs and the running parameters. 
The remaining derivatives $\partial q_k /\partial p$ must be determined using the

@@

v_i/\partial p$ and $\partial q_k/\partial p$. The effects of radiative corrections
may be easily included by including the Coleman-Weinberg potential
contributions $\Delta V$ in the EWSB conditions.\\
Evaluating the derivatives

@@

As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm} the severity of the tunings varies quite
a bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These charges change the
value of the coefficient $d$ in Eq.~(\ref{eq:originalE6MZequation}).
The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
is $\{-0.01, 0.40, 0.50, 0.81 \}$ for $\{U(1)_I, U(1)_N, U(1)_\psi,
U(1)_\eta \}$ and this determines which of the models are most tuned.

@@

with $f_1,f_2,f_3$ as given in Eq.~(\ref{eq:E6EWSBConditions}). The relevant partial derivatives are

@@

It is straightforward to compute the appropriate derivatives directly from the EWSB conditions (\ref{eq:E6EWSBConditions}). Similarly, the quantity $C$ appearing in Eq.~(\ref{eq:E6masterformula}) is given by

@@

approximated by a Taylor series, Eq.~(\ref{eq:rgeapproxsoln}).  For a

@@

diagonal, and the gaugino masses are taken to be real.\\
In the
